A Detection of the Environmental Dependence of the Sizes and Stellar Haloes of Massive Central Galaxies

### 2017-11-16 draft/paper2_v6.tex
Major changes

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}}
\def\cmodel{\texttt{cModel}}
% Samples
\def\rbcg{\texttt{cenHighMh}}
\def\nbcg{\texttt{cenLowMh}}
\def\redbcg{{$\lambda \ge 30$}}
\def\nonbcg{{$\lambda < 20$}}
% Mass related 
\def\mstar{{$M_{\star}$}}
\def\mhalo{{$M_{\mathrm{200b}}$}}
\def\logms{{$\log (M_{\star}/M_{\odot})$}}
\def\logmh{{$\log (M_{\mathrm{200b}}/M_{\odot})$}}
\def\logmhalo{{$\log (M_{\mathrm{200b}}/M_{\odot})$}}

@@

\def\logminn{{$\log (M_{\star,10\mathrm{kpc}}/M_{\odot})$}}
\def\logmtot{{$\log (M_{\star,100\mathrm{kpc}}/M_{\odot})$}}
\def\logmout{{$\log (M_{\star,150\mathrm{kpc}}/M_{\odot})$}}
\def\logmmax{{$\log (M_{\star,\mathrm{Max}}/M_{\odot})$}}
\def\logmgama{{$\log (M_{\star,\mathrm{GAMA}}/M_{\odot})$}}
\def\logmcmodel{{$\log (M_{\star,\mathrm{cModel}}/M_{\odot})$}}

@@

    This paper is organized as follows. 
    In \S \ref{sec:data} we briefly introduce the sample selection and the data 
    reduction processes.  
    Please refer to \citet{hscMassiveI} for more technical details.
    Our main results are presented in \S \ref{sec:result} and discussed in 
    \S \ref{sec:discussion}. 
    Section \S \ref{sec:summary} presents our summary and conclusions.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{
          Three-color images for a subsample of massive galaxies at $z{\sim}0.4$. 
          All of these massive galaxies have very similar \mstar{} within a 10 kpc 
          elliptical aperture 
          ($11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
          The dash-line circle at the top-left figure indicates $R=$10 kpc.
          These galaxies are rank-ordered from top to bottom and from left to right 
          by their \mstar{} within a 100 kpc elliptical aperture which varies 
          from $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$. 
          At fixed ``inner'' mass (\minn{}), massive galaxies display significant
          diversity in their outer profiles. 
          Red boxes indicate galaxies from dark matter haloes that are more massive 
          than ${\sim} 10^{14.0} M_{\odot}$. 
          }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    % Not sure we need this? Seems too off hand
    %    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    %    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).

@@

    First, we ask whether the \mden{} profiles of massive central galaxies depend on 
    halo mass at fixed stellar mass.
    %To ask this question, however, we must first define which stellar mass exactly is 
    %being fixed in the comparison.

    We will show comparisons of \mden{} profiles at both fixed \mtot{} as well as fixed 
    \minn{}. 
    We also ensure that all comparisons are performed with fixed underlying redshift
    distribution by matching samples in redshift in addition to stellar mass
    (please see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
    and Fig~\ref{fig:match} for details).

    %    The similar distributions of redshift of the matched samples ensure that the 
    %    median \mden{} profiles from both samples are affected by seeing and background 
    %    subtraction to the same extent.

@@

    We perform several statistical tests to demonstrate that the differences we see in 
    the median \mden{} profiles are significant. 
    We also conduct a variety of tests that verify the robustness of these results with
    respect to the choices of \mtot{} bins, $\lambda$ cut, the redshift range, and the 
    choice of apertures used for the metric masses. 
    Please see Appendix~\ref{app:robust} for further details.

@@

        \item For the \mtot{}--matched samples, although there is a clear and robust 
            difference between the two median \mden{} profiles, the overall difference 
            is quite subtle, especially in the inner region. 
            The difference becomes more apparent at $R>50$ kpc scales.

        \item At fixed \mtot{}, central galaxies in more massive dark matter haloes 
            display shallower \mden{} profiles compared to those living in low mass 
            dark matter haloes (they have a flatter inner \mden{} profiles and 
            more significant outer stellar haloes. 
            The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
            each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
            ($R_{\mathrm{e}}$) of massive galaxies with \logmtot{}$>11.7$--11.8.

@@

    The logarithmic scale of \mden{} on the Y-axis is partially responsible for the 
    subtle differences we see in the fixed \mtot{} comparison.  
    In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we present the same 
    comparison using the curve--of--growth of \mstar{} and the fraction of \mtot{} 
    enclosed in elliptical apertures with different radius. 
    Both of the illustrate the same results from slightly different angles. 
    They also both suggest that, at fixed \mtot{}, the environmental dependence of 
    \mden{} profiles is indeed quite subtle. 
    This may explain why previous attempts to detect such dependence using shallower 
    images often failed. 
    More importantly, this result also suggests that halo mass does not play the 
    central role in shaping massive central galaxies \textbf{at fixed ``total'' 
    stellar mass}.
    Also, the differences in median \mden{} profiles seem to become more prominent 
    at higher \mtot{}. 
    This is demonstrated in Appendix~\ref{app:robust} (see Fig~\ref{fig:prof_2}). 
    Although this trend still needs to be confirmed by larger samples, it 
    potentially indicates that the assembly of stellar haloes in more massive 
    central galaxies become more sensitive to their environments.

    Meanwhile, the comparison of \mden{} profiles at fixed \minn{}--a reasonable 
    tracer for the stellar mass in the \textit{in situ} component (right panel of 
    Fig~\ref{fig:prof_1}) hints that the inner region ($<10$ kpc) and the outer 
    stellar halo could be shaped by distinctive physical processes, and may explain 
    why they depend on halo mass differently.  
    In simulations, intensive dissipative process helps create 
    self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
    merging history leads to shallower stellar halo profile for central galaxy 
    of more massive halo (e.g. \citealt{Pillepich2014}). 
    The scatter of halo assembly histories at fixed halo mass and the stochastic 
    nature of the galaxy--galaxy mergers also explain the large \textit{intrinsic} 
    scatter in the outer \mden{} profiles and the diversity seen on the 
    \mtot{}--\minn{} plane (Fig~\ref{fig:m100_m10_color}).

    \textbf{In summary, we reliably detect subtle, but systematic \mhalo{}-dependence 
    (environmental dependence) of \mden{} profiles within 100 kpc in massive central 
    galaxies. 
    Such dependence seems to be consistent with the expectation of more (minor) 
    mergers in more massive dark matter haloes. 
    Non-dissipative (minor) mergers should not strongly alter the inner \mden{} 
    profiles, but can build up the outer halo efficiently
    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013})}.

@@

    The tight relation between \mstar{} and effective radius (or half-light radius; 
    $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$; e.g. \citealt{Shankar2013, Leja2013, 
    vdWel2014}) is one of the most important scaling relation for ETGs. 
    Despite numerous attempts, previous studies have failed to detect the 
    \mhalo{}--dependence of the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
    (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
    except for recent result by \citealt{Yoon2017}).

    The previous section clearly showed that the \mden{} profiles of massive central 
    galaxies depend on the masses of their host dark matter haloes. 
    We now ask whether or not this dependence is also manifest when considered in 
    terms of the more traditionally studied \mstar{}--$R_{\mathrm{e}}$ relation. 
    However, when considering the mass-size relation, there is ambiguity and there are
    multiple approaches to define ``sizes''. 
    This is especially relevant in the context of massive galaxies with extended 
    stellar haloes (a reason why we prefer to show \mden{} profiles directly as in 
    the previous section). 
    In this section, we still use \mtot{} as proxy of ``total'' \mstar{} and we adopt 
    the radius enclosing 50\% of stellar mass within 100 kpc ($R_{\mathrm{50}}$; 
    derived from the $i$-band curve-of-growth) as the ``size''. 
    This definition of ``effective radius'' is more robust against structural details, 
    choice of model, and the background subtraction compared to the effective radius 
    estimated by simple 2-D modeling method (e.g. single-\ser{} model). 
    Massive galaxies from this sample are large enough that the impact of seeing is 
    not a concern.

    The left panel of Fig~\ref{fig:scaling_relation} shows the 
    \mtot{}--$R_{\mathrm{50}}$ relations for galaxies in more and less massive
    dark matter haloes. 
    We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
    $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler 
    (\citealt{Emcee})\footnote{The initial guesses are based on maximum 
    likelihood estimates, and we assume flat priors for parameters.}.

@@

    \begin{equation}
        \begin{aligned}
        \log (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.74\pm0.13) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(7.56\pm1.56)
        \end{aligned}
    \end{equation}

@@

    \begin{equation}
        \begin{aligned}
        \log (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.68\pm0.06) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(6.88\pm0.75)
        \end{aligned}
    \end{equation}

    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, 
    galaxies in more and less massive dark matter haloes lie on 
    \mtot{}--$R_{\mathrm{50}}$ relations that have similar slopes but 
    different normalizations. 
    The best-fit mass--size relations derived here suggests that, 
    at $0.3 < z < 0.5$, central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.0$
    haloes are on average $\sim20$\% larger than the centrals from \logmhalo{}$<14.0$
    haloes at fixed \mtot{}.
    This result is robust against the ranges of \mstar{} over which the fit is 
    performed and against the definitions of  ``total'' \mstar{} and half-light 
    radius\footnote{Using \mstar{} within 120 or 150 kpc, or using the 
    $R_{\mathrm{50}}$ derived within these apertures do not change the results.}. 
    Given the uncertainties of the best-fit parameters, the differences in 
    mass--size relation is not very significant.  
    It relates to the relative small sample sizes, uncertainties in \mstar{} and 
    \mhalo{} estimates, and the limited \mtot{} range used in the fitting.

    We qualitatively compare our results with \citealt{HCompany13} (HC13; 
    green solid line) who studied $z\leq 0.09$ central ETGs in 
    $12.5 \le$ \logmh{} $< 15$ haloes. 
    HC13 use the group catalogue by \citet{Yang2007} to estimate halo mass. 
    They obtain effective radii from single-\ser{} model fitting to SDSS 
    images and \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
    synthetic population model. 
    We convert their \mstar{} estimates from a Kroupa IMF to a Chabrier 
    IMF by applying a constant -0.05 dex shift (see \citealt{Bernardi2016a}). 
    We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
    offset between BC03 and our FSPS model (see Paper~1). 
    The distributions of galaxies on the 
    \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
    (with slightly shallower slopes), even at \logmtot{}$< 11.6$ where our samples 
    start to become incomplete in stellar mass. 
    In contrast to the present study, HC13 finds no environment dependence in the 
    mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$.     
    Both the considerably shallower SDSS images and the single-\ser{} model could 
    contribute to this difference, since the most clear environmental differences 
    are found in the low surface brightness stellar haloes that can not be 
    well-modeled with the inner portion of the \mden{} profile using single-\ser{}
    profiles.

    In conclusion, we confirm that the \mtot{}--$R_{\mathrm{50}}$ relation of massive
    central galaxies at $0.3 < z < 0.5$ depends on halo mass. 
    At fixed \mtot{}, massive central galaxies in denser environments (higher \mhalo{}) 
    have larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
    \mtot{}. 
%% ------------------------------------------------------------------------------------ %%

@@

    \begin{equation}
        \begin{aligned}
        \log (M_{\star, 10\ \mathrm{kpc}}/M_{\odot}) = & (0.48\pm0.06) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & +(5.72\pm0.75).
        \end{aligned}
    \end{equation}

@@

    \begin{equation}
        \begin{aligned}
        \log (M_{\star, 10\ \mathrm{kpc}}/M_{\odot}) = & (0.56\pm0.03) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & +(4.82\pm0.30).
        \end{aligned}
    \end{equation}

@@

%    The \mtot{}--$M_{\star, 5\ \mathrm{kpc}}$ relation actually suggests clearer 
%    \mhalo{}-dependence at high-\mtot{} end, but the $M_{\star, 5\ \mathrm{kpc}}$ 
%    are more vulnerable to the impact from seeing than \minn{}.

    From Figure \ref{fig:scaling_relation} we can draw the same conclusions as in 
    the previous section, namely that: 
    at fixed \mtot{}, central galaxies in more massive haloes tend to have smaller 
    fraction of stellar mass in their inner regions and higher \mstar{} in their outer
    stellar haloes. 
    Meanwhile, at fixed \minn{}--a proxy for the \mstar{} of the ``in situ'' component,
    central galaxies in more massive haloes tend to be more massive and display more 
    prominent stellar haloes. 
    The scientific implication of these results will be discussed in 
    Section~\ref{sec:discussion}.

    % Although the HSC images can not resolve the central region of these massive 
    % galaxies, the on average lower \mstar{} within 10 kpc and shallower inner \mden{} 
    % profile for massive central galaxies living in more massive haloes are robust 
    % results and could have interesting physical implications.

@@

    Besides these conclusions, the fact that we find smooth ellipticity profiles and 
    shallow gradients favors the idea of using the flux-weighted average isophotal 
    shape to extract 1-D \mden{} profiles of massive galaxies. 
    The similarity of average rest-frame color profiles between the \rbcg{} and \nbcg{}
    samples suggests that \mden{} profiles based on single average \m2l{} will not bias 
    our comparisons.

@@

    At the same time, from the comparison of median \mden{} profiles of the 
    \mtot{}--matched samples and from the \mtot{}--\minn{} plane, our results also 
    show that the centrals of more massive haloes have slightly shallower inner 
    \mden{} slope and lower fraction of \mtot{} within the inner 10 kpc.
    It seems that the environmental dependence of stellar mass distributions in 
    massive central galaxies also affects their central region.
    This is not caused by the choice of outer aperture to estimate ``total''
    \mstar{}: assuming that centrals in more massive haloes have more extended 
    \mden{} profiles, integration out to larger aperture will make the differences 
    between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} plane more 
    significant.

>>>>

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}}
\def\cmodel{\texttt{cModel}}
% Samples
\def\rbcg{\texttt{cenHighMh}}
\def\nbcg{\texttt{cenLowMh}}
\def\redbcg{{$\lambda \ge 30$}}
\def\nonbcg{{$\lambda < 20$}}
% Mass related 
\def\mstar{{$M_{\star}$}}
\def\mhalo{{$M_{\mathrm{200b}}$}}
\def\logms{{$\log_{10} (M_{\star}/M_{\odot})$}}
\def\logmh{{$\log_{10} (M_{\mathrm{200b}}/M_{\odot})$}}
\def\logmhalo{{$\log_{10} (M_{\mathrm{200b}}/M_{\odot})$}}

@@

\def\logminn{{$\log_{10} (M_{\star,10\mathrm{kpc}}/M_{\odot})$}}
\def\logmtot{{$\log_{10} (M_{\star,100\mathrm{kpc}}/M_{\odot})$}}
\def\logmout{{$\log_{10} (M_{\star,150\mathrm{kpc}}/M_{\odot})$}}
\def\logmmax{{$\log_{10} (M_{\star,\mathrm{Max}}/M_{\odot})$}}
\def\logmgama{{$\log_{10} (M_{\star,\mathrm{GAMA}}/M_{\odot})$}}
\def\logmcmodel{{$\log_{10} (M_{\star,\mathrm{cModel}}/M_{\odot})$}}

@@

    This paper is organized as follows. 
    In \S \ref{sec:data} we briefly introduce the sample selection and the data 
    reduction processes.  
    Please refer to \citet{hscMassiveI} for more technical details.
    Our main results are presented in \S \ref{sec:result} and discussed in 
    \S \ref{sec:discussion}. 
    \S \ref{sec:summary} presents our summary and conclusions.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{
          Three-color images for a subsample of massive galaxies at $z{\sim}0.4$. 
          All of these massive galaxies have very similar \mstar{} within a 10 kpc 
          elliptical aperture 
          ($11.2<\log_{10} (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
          The dash-line circle at the top-left figure indicates $R=$10 kpc.
          These galaxies are rank-ordered from top to bottom and from left to right 
          by their \mstar{} within a 100 kpc elliptical aperture which varies 
          from $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$. 
          At fixed ``inner'' mass (\minn{}), massive galaxies display significant
          diversity in their outer profiles. 
          Red boxes indicate galaxies from dark matter haloes that are more massive 
          than ${\sim} 10^{14.0} M_{\odot}$. 
          }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

@@

    First, we ask whether the \mden{} profiles of massive central galaxies depend on 
    halo mass at fixed stellar mass.    
    We will show comparisons of \mden{} profiles at both fixed \mtot{} as well as fixed 
    \minn{}. 
    We also ensure that all comparisons are performed with fixed underlying redshift
    distribution by matching samples in redshift in addition to stellar mass
    (please see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
    and Fig~\ref{fig:match} for details).

@@

    \song{
    We estimate the uncertainties of the median \mden{} profiles using bootstrap 
    resampling test. 
    We also perform statistical tests to demonstrate that the differences of \mden{}
    profiles are more significant than the levels allowed by the intrinsic randomness
    within the combined \rbcg{} and \nbcg{} sample. 
    }
    We also conduct a variety of tests that verify the robustness of these results with
    respect to the choices of \mtot{} bins, $\lambda$ cut, the redshift range, and the 
    choice of apertures used for the metric masses. 
    Please see Appendix~\ref{app:robust} for further details.

@@

        \item \song{
            For the \mtot{}--matched samples, there are some subtle but statistically 
            significant and robust differences between the two median \mden{} profiles.
            Due to the logarithmic scale, the difference in the inner region appears 
            to be very small. 
            Meanwhile, the difference in \mden{} profile becomes more apparent 
            at $R>50$ kpc scales.  
            In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we compare the same
            \mtot{}--matched samples using the cumulative \mstar{} profiles 
            (or `curve of growth') and the fraction of \mtot{} enclosed within 
            different radius.
            Both comparisons highlight the differences in median \mden{} profiles 
            from different angles.
            }

        \item At fixed \mtot{}, central galaxies in more massive dark matter haloes 
            display shallower \mden{} profiles compared to those from less massive 
            dark matter haloes (they have a flatter inner \mden{} profiles and 
            more significant outer stellar haloes. 
            The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
            each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
            ($R_{\mathrm{e}}$) of massive galaxies with \logmtot{}$>11.7$--11.8.

@@

    \song{
    The subtle differences seen on the left side of Fig \ref{fig:prof_1} suggests
    that the stellar mass distributions of the most massive central galaxies only
    weakly depend on their environments. 
    }
    This may explain why previous attempts to detect such dependence using 
    shallower images often failed. 
    More importantly, this result also suggests that halo mass does not play the 
    central role in shaping massive central galaxies \textbf{at fixed ``total'' 
    stellar mass}.
    Also, the differences in median \mden{} profiles seem to become more prominent 
    at higher \mtot{}. 
    This is demonstrated in Appendix~\ref{app:robust} (see Fig~\ref{fig:prof_2}). 
    Although this trend still needs to be confirmed by larger samples, it 
    potentially indicates that the assembly of stellar haloes in more massive 
    central galaxies become more sensitive to their environments.

    \song{
    Meanwhile, the comparison of \mden{} profiles at fixed \minn{}--a potential 
    tracer of the \mstar{} in the \textit{in situ} component (right panel of 
    Fig~\ref{fig:prof_1}) hints that the inner region ($<10$ kpc) and the outer 
    stellar halo are shaped by different physical processes and response to 
    environment at different levels. 
    }  
    In hydrodynamic simulations, intense dissipative processes help create 
    self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
    merging history leads to shallower stellar halo profile for central galaxy 
    of more massive halo (e.g. \citealt{Pillepich2014}). 
    The intrinsic scatter of halo assembly histories at fixed halo mass and the 
    stochastic nature of the galaxy--galaxy mergers also explain the large 
    \textit{intrinsic} scatter in the outer \mden{} profiles and the diversity 
    seen on the \mtot{}--\minn{} plane (Fig~\ref{fig:m100_m10_color}).

    \textbf{In summary, we reliably detect subtle, but systematic \mhalo{}-dependence 
    (environmental dependence) of \mden{} profiles within 100 kpc in massive central 
    galaxies. 
    Such dependence seems to be consistent with the expectation of more (minor) 
    mergers in more massive dark matter haloes. 
    Non-dissipative (minor) mergers should not strongly alter the inner \mden{} 
    profiles, but can build up the outer halo efficiently
    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013})}.
    \song{
    As for the inner \mden{} profiles, although the comparison of the \minn{}-matched
    samples reveals clear differences, we should point out that several physical 
    processes could alter \minn{} and the \mden{} profiles within 10 kpc during the
    last 10 Gyrs (e.g., AGN feedback or merger of binary supermassive black holes). 
    We will further discuss this in \S~\ref{ssec:cen}.
    }

@@

    The tight relation between \mstar{} and effective radius (or half-light radius; 
    $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$; e.g. \citealt{Shankar2013, Leja2013, 
    vdWel2014}) is one of the most important scaling relation for ETGs. 
    Despite numerous attempts, previous studies have failed to detect the 
    \mhalo{}--dependence of the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
    (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
    except for the recent result by \citealt{Yoon2017}).

    \song{
    In the previous section, the differences in the \mden{} profiles already reveals 
    that the \mtot{}-matched massive galaxies from different environments should have
    different effective radius (especially see Fig~\ref{fig:cog}). 
    We now specifically look into the more traditionally studied 
    \mstar{}--$R_{\mathrm{e}}$ relation.
    Firstly, we want to point out that `size' is not a well defined parameter for 
    object like massive galaxies with very extended stellar mass distributions. 
    In practice, the measurements of `effective radius' or `half--light radius' 
    not only depends on resolution, depth, and filter of the image, but may also 
    depend on the adopted model for the light profile.  
    This makes comparisons of size measurements among different observations 
    or between observations and models much more uncertain, and is the main reason
    why we prefer to compare the \mden{} profiles directly.
    }
    In this section, we still use \mtot{} as proxy of ``total'' \mstar{} and we adopt 
    the radius enclosing 50\% of stellar mass within 100 kpc ($R_{\mathrm{50}}$; 
    derived from the $i$-band curve-of-growth) as the ``size''. 
    Such definition of ``half--light radius'' is more robust against structural 
    details, choice of model, and the background subtraction compared to the 
    effective radius measured using 2-D model with oversimplified assumptions 
    (e.g. single-\ser{} model). 
    Massive galaxies in this sample are large enough so that the impact of seeing 
    is not a concern.

    The left panel of Fig~\ref{fig:scaling_relation} shows the 
    \mtot{}--$R_{\mathrm{50}}$ relations for galaxies in more and less massive
    dark matter haloes. 
    We fit the \logmtot{}-$\log_{10} (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
    $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler 
    (\citealt{Emcee}) \footnote{The initial guesses are based on maximum 
    likelihood estimates, and we assume flat priors for parameters.}.
    \song{
    Uncertainties in both \mtot{} and $R_{\mathrm{50}}$ are considered. 
    For \logmtot{}$>11.6$ galaxies, typical uncertainty for mass is $\sim 0.12$
    dex.  
    As for the $R_{\mathrm{50}}$, its uncertainty based on the \mden{} profile
    is very small due to the high \s2n{} of the profile. 
    We manually assign 10\% error for $R_{\mathrm{50}}$. 
    }

@@

    \begin{equation}
        \begin{aligned}
        \log_{10} (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.74\pm0.13) \times \log_{10} (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(7.56\pm1.56)
        \end{aligned}
    \end{equation}

@@

    \begin{equation}
        \begin{aligned}
        \log_{10} (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.68\pm0.06) \times \log_{10} (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(6.88\pm0.75)
        \end{aligned}
    \end{equation}

    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, 
    massive central galaxies of more and less massive dark matter haloes lie on 
    \mtot{}--$R_{\mathrm{50}}$ relations that have similar slopes but 
    different normalizations. 
    The best--fit mass--size relations derived here suggests that, 
    at $0.3 < z < 0.5$, central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.2$
    haloes are on average $\sim20$\% larger than the centrals from \logmhalo{}$<14.0$
    haloes at fixed \mtot{}.
    This result is robust against the ranges of \mstar{} over which the fit is 
    performed and against the definitions of  ``total'' \mstar{} and half-light 
    radius\footnote{Using \mstar{} within 120 or 150 kpc, or using the 
    $R_{\mathrm{50}}$ derived within these apertures do not change the results.}. 
    \song{
    Due to the relative steep slopes for the \mtot{}--$R_{\mathrm{50}}$ relation, 
    secondary binning (e.g., different halo mass) may induce artificial differences
    (e.g., \citealt{Sonnenfeld2017}). 
    We first check the results using the \mtot{}--matched samples and confirm 
    the above conclusion. 
    Furthermore, a normalized size parameter ($\gamma$; e.g., \citealt{Newman2012, 
    HCompany13}) is proposed to control this effect. 
    We follow the definition of $\gamma$ in \citet{HCompany13}:
    }

    \begin{equation}
        \log_{10}(\gamma) = \log_{10} (R_{\mathrm{50}}) + \beta (11 - \log_{10}M_{\star, 100\ \mathrm{kpc}}),
    \end{equation}

    \song{
    where $\beta$ is the slope of the mass--size relation.
    For the \logmtot{}$>11.6$ galaxies, we estimate the average $\gamma$ of both
    samples using the slopes of their best--fit mtot{}--$R_{\mathrm{50}}$ relations.
    For the \rbcg{} sample, $<\gamma> = 4.2\pm0.4$; for the \nbcg{} one, 
    $<\gamma> = 3.8\pm0.3$. 
    Although the uncertainty is still quite large mainly due to the relative small 
    sample size, the result also suggests a more significant environmental dependence
    of $R_{\mathrm{50}}$ at fixed stellar mass compared to the \citet{HCompany13} 
    one.
    Given the uncertainties involved, the dependence of $R_{\mathrm{50}}$ of 
    massive central galaxies at fixed \mtot{} is not very significant and is much 
    weaker than the predictions of certain models in \citet{Shankar2014}. 
    But before we rule out these models, we need to mention that the uncertainties 
    of both mass and size are capable of washing out signals of stronger 
    environment--dependence as shown in \citet{HCompany13}.
    Therefore we think the direct comparison of \mden{} profiles or the 
    \mtot{}--\minn{} relation may be better at tracing the environment dependence
    of structure in massive galaxies. 
    }

    We qualitatively compare our results with \citealt{HCompany13} (HC13; 
    green solid line) who studied $z\leq 0.09$ central ETGs in 
    $12.5 \le$ \logmh{} $< 15$ haloes. 
    HC13 use the group catalogue by \citet{Yang2007} to estimate halo mass. 
    They obtain effective radii from single-\ser{} model fitting to SDSS 
    images and \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
    synthetic population model. 
    We convert their \mstar{} estimates from a Kroupa IMF to a Chabrier 
    IMF by applying a constant -0.05 dex shift (see \citealt{Bernardi2016a}). 
    We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
    offset between BC03 and our FSPS model (see Paper~1). 
    The distributions of our massive galaxies on the \mtot{}--$R_{\mathrm{50}}$ 
    plane follow the HC13 relation reasonably well (with slightly shallower slopes), 
    even at \logmtot{}$< 11.6$ where our samples start to become incomplete in \mtot{}. 
    In contrast to the present study, HC13 finds no environment dependence in the 
    mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$. 
    \song{
    This could relate to the difference in the depth of HSC and SDSS images.
    The very low surface brightness stellar haloes that show clearly 
    environment dependence in this work are difficult to see or model on SDSS images.        
    And, given the much shallower SDSS images used in HC13, it is a little bit 
    surprised to see that their mass-size relation is not very different with the
    ones using deeper HSC images. 
    Besides the systematics in the \m2l{} estimates using different methods, 
    different photometric methods could be the main reason behinds this 
    coincidence.
    For instance, if shallower image leads to systematically underestimated mass, 
    it could shift the mass--size relation horizontally.  
    And single-\ser{} is not very accurate model for massive galaxies, hence it 
    can result in bias of both mass and size measurements (e.g., see 
    Appendix~\ref{app:gama}). 
    This further reflects our point that `size' is not straightforward to measure 
    and compare, also that the mass--size relation may not be the best tool to 
    investigate environment dependence in massive galaxies. 
    }

    In conclusion, we confirm that the \mtot{}--$R_{\mathrm{50}}$ relation of massive
    central galaxies at $0.3 < z < 0.5$ weakly depends on halo mass. 
    At fixed \mtot{}, massive central galaxies in denser environments (higher \mhalo{}) 
    have larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
    \mtot{}. 
%% ------------------------------------------------------------------------------------ %%

@@

    \begin{equation}
        \begin{aligned}
        \log_{10} (M_{\star, 10\ \mathrm{kpc}}/M_{\odot}) = & (0.48\pm0.06) \times \log_{10} (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & +(5.72\pm0.75).
        \end{aligned}
    \end{equation}

@@

    \begin{equation}
        \begin{aligned}
        \log_{10} (M_{\star, 10\ \mathrm{kpc}}/M_{\odot}) = & (0.56\pm0.03) \times \log_{10} (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & +(4.82\pm0.30).
        \end{aligned}
    \end{equation}

@@

    From Figure \ref{fig:scaling_relation} we can draw the same conclusions as in 
    the previous section, namely that: 
    at fixed \mtot{}, central galaxies in more massive haloes tend to have smaller 
    fraction of stellar mass in their inner regions and higher \mstar{} in their outer
    stellar haloes. 
    Meanwhile, at fixed \minn{}--a proxy for the \mstar{} of the ``in situ'' component,
    central galaxies in more massive haloes tend to be more massive and display more 
    prominent stellar haloes. 
    \song{
    The comparison of \mden{} profiles for \minn{}--matched samples may not directly
    reflects the environment related processes as other physical mechanisms could 
    also change the inner \mden{} profiles and their \mtot{} could be quite different. 
    But the combination of \mtot{} and \minn{} clearly suggests that information of
    their dark matter haloes or environments is encoded within this simple 2--D plane. 
    We will discuss more scientific implications of these results in 
    \S~\ref{sec:discussion}
    }

@@

    Besides these conclusions, the fact that we find smooth ellipticity profiles and 
    shallow gradients favors the idea of using the flux-weighted average isophotal 
    shape to extract 1-D \mden{} profiles of massive galaxies. 
    The similarity of average rest-frame color profiles between the \rbcg{} and \nbcg{}
    samples suggests that \mden{} profiles based on single average \m2l{} will not bias 
    our comparisons. 
    \song{
    At the same time, we are not certain that similar conclusions apply to the 
    color or ellipticity profiles within the inner 5--6 kpc due to the smearing effect
    of the seeing. 
    Central color gradients may be sensitive to other physical processes and deserves 
    future investigation using 2-D modelling method and/or image with higher spatial 
    resolution.
    }

@@

    At the same time, from the comparison of median \mden{} profiles of the 
    \mtot{}--matched samples and from the \mtot{}--\minn{} plane, our results also 
    show that the centrals of more massive haloes have slightly shallower inner 
    \mden{} slope and lower fraction of \mtot{} within the inner 10 kpc.
    \song{
    This can not be solely explained by the choice of a finite aperture to 
    estimate ``total'' \mstar{}: assuming that centrals from more massive haloes 
    have more extended \mden{} profiles, integration out to larger aperture will 
    make the differences between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} 
    plane even more significant.
    }
